---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dqtools

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

TAF data users often need to assess the feasibility of specific data analytic 
tasks. One typical workflow is to first specify the TAF file types, states, 
years, and variables of interest, and then check the fantastic 
[DQ Atlas](https://www.medicaid.gov/dq-atlas/welcome) site for potential data 
quality (DQ) concerns. 

The goal of `dqtools` is to simplify the second step for experienced TAF users 
by providing a state-year-variable level assessment for different TAF file types 
made available by DQ Atlas.

## Installation

You can install the development version of `dqtools` like so:

``` r
# install.packages("remotes")
remotes::install_github("jjchern/dqtools")
```

## Example

```{r example, message=FALSE}
library(dplyr)

dqtools::dq_ip_file

dqtools::dq_ip_file |> count(Variable)

dqtools::dq_ip_file |> count(Topic)

dqtools::dq_ip_file |> count(Topic, `DQ Assessment`)
```
